% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 

\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}
\usepackage{CJKutf8}

\CJKencfamily{UTF8}{bkai}

\AtBeginDocument{%
    \begin{CJK}{UTF8}{bkai}} 
    \AtEndDocument{%
    \clearpage\end{CJK}}

\title{iWildCam 2019 - FGVC6}

% A subtitle is optional and this may be deleted
\subtitle{Categorize animals in the wild}

\author{F.~黃騰陞\inst{1} \and S.~吳宗晉\inst{2} \and T.~施紹唐\inst{3}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Universities of Somewhere and Elsewhere] % (optional, but mostly needed)
{
  \inst{1}%
  Department of Computer Science\\
  University of Yuan Ze
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date{開放平台軟體期末專題, 2019}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{Theoretical Computer Science}
% This is only inserted into the PDF information catalog. Can be left
% out. 

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}
\begin{CJK}{UTF8}{}
\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
\setcounter{tocdepth}{1}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\subsection{成員介紹}

\begin{frame}{Introduction}{成員介紹}
  \begin{itemize}
  \item {
    1043362　黃騰陞
  }
  \item {
    1041562　吳宗晉

  }
  \item {
    1043310　施紹唐	
  }
  \end{itemize}
\end{frame}

\subsection{專題問題描述}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{Introduction}{專題問題描述}
  \begin{itemize}
  \item {
    First item.
    \pause % The slide will pause after showing the first item
  }
  
  \end{itemize}
\end{frame}

\section{Methodology}

\subsection{Input of model}

\begin{frame}{Methodology}{Input of model}
	\begin{itemize}
	\item{
		Input of model
	}
	
	
	\end{itemize}
\end{frame}

\subsection{Output of model}

\begin{frame}{Methodology}{Output of model}
	\begin{itemize}
	\item{
		Output of model
	}
	\end{itemize}
\end{frame}

\subsection{Layers of model}

\begin{frame}{Methodology}{Layers of model}
	\begin{itemize}
	\item{
		Output of model
	}
	\end{itemize}
\end{frame}

\subsection{Model save}

\begin{frame}{Methodology}{Model save}
	\begin{itemize}
	\item{
		Model save
	}
	\end{itemize}
\end{frame}

\subsection{File size of model}

\begin{frame}{Methodology}{File size of model}
	\begin{itemize}
	\item{
		File size of model
	}
	\end{itemize}
\end{frame}

\subsection{Loss function}

\begin{frame}{Methodology}{Loss function}
	\begin{itemize}
	\item{
		Loss function
	}
	\end{itemize}
\end{frame}

\subsection{Optimizer and hyperparameter}

\begin{frame}{Methodology}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		Optimizer and hyperparameter
	}
	\end{itemize}
\end{frame}

\section{Dataset}

\subsection{Size of dataset}

\begin{frame}{Dataset}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		Size of dataset
	}
	\end{itemize}
\end{frame}v

\subsection{資料集來源}

\begin{frame}{Dataset}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		資料集來源
	}
	\end{itemize}
\end{frame}

\subsection{訓練樣本數量}

\begin{frame}{Methodology}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		訓練樣本數量
	}
	\end{itemize}
\end{frame}

\subsection{驗證樣本數量}

\begin{frame}{Dataset}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		驗證樣本數量
	}
	\end{itemize}
\end{frame}

\subsection{測試樣本數量}

\begin{frame}{Dataset}{Optimizer and hyperparameter}
	\begin{itemize}
	\item{
		測試樣本數量
	}
	\end{itemize}
\end{frame}

\section{Experimental Evaluation}

\subsection{Experimental environment}

\begin{frame}{Experimental Evaluation}{Experimental environment}
	\begin{itemize}
	\item{
		Experimental environment
	}
	\end{itemize}
\end{frame}

\subsection{Epochs of training}

\begin{frame}{Experimental Evaluation}{Epochs of training}
	\begin{itemize}
	\item{
		Epochs of training
	}
	\end{itemize}
\end{frame}

\subsection{Qualitative evaluation}

\begin{frame}{Experimental Evaluation}{Qualitative evaluationQualitative evaluation}
	\begin{itemize}
	\item{
		Qualitative evaluation
	}
	\end{itemize}
\end{frame}

\subsection{Quantitative evaluation}

\begin{frame}{Experimental Evaluation}{Quantitative evaluation}
	\begin{itemize}
	\item{
		Quantitative evaluation
	}
	\end{itemize}
\end{frame}


\begin{frame}{Blocks}
\begin{block}{Block Title}
You can also highlight sections of your presentation in a block, with it's own title
\end{block}
\begin{theorem}
There are separate environments for theorems, examples, definitions and proofs.
\end{theorem}
\begin{example}
Here is an example of an example block.
\end{example}
\end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}
  
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}



% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{For Further Reading}
    
  \begin{thebibliography}{10}
    
  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.
 
    
  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short. 

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}
\end{CJK}
\end{document}


